Trends of SDR in Thessaloniki

### 2023-07-08 Article.Rmd
Commit 2023-07-08 20:14

@@

>>>>

Cumulative sum [@Regier2019]

@@

<!-- ```{r cumsumSTD, echo = FALSE, fig.cap='two plots', fig.subcap=c('one plot', 'the other one'), out.width='.32\\linewidth', fig.asp=1, fig.ncol = 3} -->
<!-- knitr::include_graphics(c( -->
<!--     "./images/CumulativeDailyCumSumSTD-1.png",    # ALL sky -->
<!--     "./images/CumulativeDailyCumSumSTD-2.png",    # CLEAR sky -->
<!--     "./images/CumulativeDailyCumSumSTD-3.png"))   # Cloud sky -->
<!-- ``` -->
